Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
ref to appendix on noise

\item Calculate the noise set $N$ from the quantizer resolutions and estimated round-off errors: %($\frac{q_1}{2},\frac{q_2}{2},q_3$)
$$N=\left \{ \nu_1+\nu_2+ \nu_3 : \nu_1 \in \left[-\frac{q1}{2}\ \ \frac{q1}{2}\right] 
\wedge \nu_2 \in \left[-\frac{q2}{2}\ \ \frac{q2}{2}\right]  \wedge \nu_3 \in \left[-q3\ \ q3\right]  \right \}\nonumber$$
where  $q_1$ is the error introduced by the truncation by the ADC, $q_2$ is the error introduced by the DAC and $q3$ is the maximum truncation and rounding error of the mathematical operation $u_k=-K\hat{x}_k$ as discussed in section \ref{sec:numeric_rep}. We consider the error introduced by the DAC to be equal to zero, since the domain of the plant is at a higher precision than the controller.
%More details on how to model quantization as noise are given in the 
%Appendix~\ref{appendix:quantization-noise}.
\item Calculate a set of initial bounds on $K$, $\phi_\mathit{init}^{K}$, based on the input constraints. Note that these bounds will be used by the {\sc synthesize} phase to reduce the size of the solution space.
$$(\phi_\mathit{init} \wedge \phi_\mathit{input} \wedge u_k=-K x_k) \Rightarrow \phi_\mathit{init}^{K}$$

@@

During any given ADC conversion, the continuous signal will be sampled in the real domain and transformed by $\mathcal{F}\langle I_{c},F_{c} \rangle (x)$ (assuming the ADC discretization is the same as the digital implementation). This sampling uses a threshold which is defined by the less significant bit ($q_{c}=2^{-F_c}$) of the ADC and some non-linearities of the circuitry. The overall conversion is
$$\mathcal{F}\langle I_{c},F_{c} \rangle(y(t)) = y_k : y_k \in \left[y(t)-\frac{q_{c}}{2}\ \ \ \ y(t)+\frac{q_{c}}{2}\right]$$
If we denote the error in the conversion as $\nu_k=y_k-y(t) : t=nk$ then we may define some bounds for it $\nu_k \in [-\frac{q_{c}}{2}\ \ \frac{q_{c}}{2}]$.

>>>>

\item Calculate the noise set $N$ from the quantizer resolutions and estimated round-off errors: %($\frac{q_1}{2},\frac{q_2}{2},q_3$)
$$N=\left \{ \nu_1+\nu_2+ \nu_3 : \nu_1 \in \left[-\frac{q1}{2}\ \ \frac{q1}{2}\right] 
\wedge \nu_2 \in \left[-\frac{q2}{2}\ \ \frac{q2}{2}\right]  \wedge \nu_3 \in \left[-q3\ \ q3\right]  \right \}\nonumber$$
where  $q_1$ is the error introduced by the truncation by the ADC, $q_2$ is the error introduced by the DAC and $q3$ is the maximum truncation and rounding error of the mathematical operation $u_k=-K\hat{x}_k$ as discussed in section \ref{sec:numeric_rep}. 
More details on how to model quantization as noise are given in the 
Appendix~\ref{appendix:quantization-noise}.
\item Calculate a set of initial bounds on $K$, $\phi_\mathit{init}^{K}$, based on the input constraints. Note that these bounds will be used by the {\sc synthesize} phase to reduce the size of the solution space.
$$(\phi_\mathit{init} \wedge \phi_\mathit{input} \wedge u_k=-K x_k) \Rightarrow \phi_\mathit{init}^{K}$$

@@

During any given ADC conversion, the continuous signal will be sampled in the real domain and transformed by $\mathcal{F}\langle I_{c},F_{c} \rangle (x)$ (assuming the ADC discretization is the same as the digital implementation). This sampling uses a threshold which is defined by the less significant bit ($q_{c}=2^{-F_c}$) of the ADC and some non-linearities of the circuitry. The overall conversion is
$$\mathcal{F}\langle I_{c},F_{c} \rangle(y(t)) = y_k : y_k \in \left[y(t)-\frac{q_{c}}{2}\ \ \ \ y(t)+\frac{q_{c}}{2}\right]$$
If we denote the error in the conversion as $\nu_k=y_k-y(t)$ where $t = nk$, and $n$ is the sampling time and $k$ the number of steps, then we may define some bounds for it $\nu_k \in [-\frac{q_{c}}{2}\ \ \frac{q_{c}}{2}]$.
